\cvsection{Experience}
\begin{cventries}
  \cventry
    {Web Development}
    {Software Engineering Intern {\entrytitleconnectorstyle{\;at\;}} VTEX}
    {Rio de Janeiro, Brazil}
    {Dec. 2020 - PRESENT}
    {
      \begin{cvitems}
        \item {Developed into production an internal application that centralizes the management of payment and anti-fraud services.}
        \item {Implemented the application in {\bodyfont TypeScript} with {\bodyfont React}, {\bodyfont Node.js} and {\bodyfont GraphQL}.}
      \end{cvitems}
    }

  \cventry
    {Mobile Development}
    {iOS Developer {\entrytitleconnectorstyle{\;at\;}} Apple Developer Academy | PUCRS}
    {Porto Alegre, Brazil}
    {Jan. 2017 - Dec. 2018}
    {
      \begin{cvitems}
        \item {Development of apps and games in {\bodyfont Swift}/{\bodyfont Objective-C} for iOS, tvOS and watchOS.}
        \item {Project management and product development of over 10 different projects using {\bodyfont Scrum}.}
        \item {Usage of {\bodyfont Challenge Based Learning}.}
      \end{cvitems}
    }

    \cventry
      {Research and Mobile Development}
      {Undergraduate Researcher {\entrytitleconnectorstyle{\;on\;}} Mobile Campimetry | CNPq}
      {Porto Alegre, Brazil}
      {Jan. 2020 - Sep. 2020}
      {
        \begin{cvitems}
          \item {Contributed to the development of a low-cost and portable instrument that performs an eye examination.}
          \item {Extended the Android application (written in Java) to correct a distortion caused by the low-cost lens utilized.}
        \end{cvitems}
      }
\end{cventries}
