\cvsection{Published Works}

%\cvsubsection{iOS Apps}
%\cvcompactentry

\begin{cventries}
  \cventry
    {A beautifully pleasant time warping shoot'em up game for ios.}
    {Chrono Division}
    {\href{https://www.youtube.com/watch?v=Wc9-ALdmvRw}{Youtube} \hspace{4pt} \href{https://itunes.apple.com/app/id1437675179}{App Store}}
    {2018}
    {
      \begin{cvitems}
        \item {Created the concept and developed the {\bodyfont Swift} code of the game alongside other 3 developers and a designer.}
        \item {Built an {\bodyfont Entity-Component-System architecture} on top of {\bodyfont SpriteKit/GameplayKit}.}
      \end{cvitems}
    }
  % \cventry
  %   {An ios/watchos app with journaling and a breathing exercise to help with anxiety or panic attacks.}
  %   {Breather}
  %   {\href{https://itunes.apple.com/app/id1370659046}{App Store}}
  %   {2018}
  %   {
  %     \begin{cvitems}
  %       \item {Designed the user interfaces and user experience in the iOS and watchOS apps.}
  %     \end{cvitems}
  %   }
  \cventry
    {Apple's swift student challenge winning game where you create music by jumping over obstacles.}
    {Beat: A Musical Journey}
    {\href{https://www.youtube.com/watch?v=ayVB08sXtZY}{Youtube} \hspace{4pt} \href{https://github.com/renanmagagnin/beat-wwdc20}{GitHub} \hspace{4pt} \href{https://apps.apple.com/br/app/beat-a-musical-journey/id1514160330}{App Store}}
    {2020}
    {
      \begin{cvitems}
        \item {Developed all of the {\bodyfont Swift} code and designed the experience and visuals of the game.}
      \end{cvitems}
    }
  % \cventry
  %   {A wwdc18 scholarship winning swift playground where the player has to fight off waves of enemies.}
  %   {Orbs}
  %   {\href{https://www.youtube.com/watch?v=W-tzS0x1SiA}{Youtube} \hspace{4pt} \href{https://github.com/renanmagagnin/orbs-wwdc18}{GitHub}}
  %   {2018}
  %   {
  %     \begin{cvitems}
  %       % \item {Developed and designed all the code and visuals in the game.}
  %       \item {Developed all of the Swift code and designed the experience and visuals of the game.}
  %     \end{cvitems}
  %   }
  \cventry
    {A game for ipad where you blow minds, literally. wwdc19 scholarship winning project.}
    {Mindblower: The Game}
    {\href{https://medium.freecodecamp.org/how-i-won-a-scholarship-to-apples-yearly-event-for-the-second-time-f04f5f4636b1}{Medium} \hspace{4pt} \href{https://www.youtube.com/watch?v=xH9cn7BtG8k}{Youtube} \hspace{4pt} \href{https://itunes.apple.com/us/app/mindblower-the-game/id1460079689}{App Store}} %\hspace{4pt} \href{https://github.com/renanmagagnin/mindblower-wwdc19}{GitHub}}
    {2019}
    {
      \begin{cvitems}
        %\item {Developed and designed all the code and visuals in the game.}
        \item {Developed all of the {\bodyfont Swift} code and designed the experience and visuals of the game.}
        \item {Wrote an article describing and reflecting on the entire creation process behind the project.}
      \end{cvitems}
    }
  % \cventry
  %   % {An ios game where you play as brazil's unpopular president, michel temer, and need to avoid protesters.}
  %   {An ios game where the player must avoid protesters as brazil's unpopular president, michel temer.}
  %   {Fora Memer}
  %   {\href{https://youtu.be/YwVg7Yuu3pY}{Youtube} \hspace{4pt} \href{https://itunes.apple.com/br/app/fora-memer/id1253655537}{App Store}}
  %   {2017}
  %   {
  %     \begin{cvitems}
  %       \item {Created the concept and developed the Swift code of the game in 3 days alongside other 2 developers and a designer.}
  %     \end{cvitems}
  %   }
\end{cventries}
